---
title: "7_2_factor careful"
author: "Hayato Yoshioka"
date: "2025-06-05"
output: html_document
---

SHAP for one factor

```{r}
require(here)
source("Script/MyFunctions.R")
library(iml)
require(ranger)
library(ggplot2)
library(igraph)
library(ggraph)
library(dplyr)
library(progress)
library(here)
library(stringr)


extract_genus <- function(tax_str, rowname) {
  # Extract genus: pattern "g__XXXX"
  genus_match <- regmatches(tax_str, regexpr("g__[^;]+", tax_str))
  
  # Remove "g__" if found
  if (length(genus_match) > 0) {
    genus <- gsub("g__", "", genus_match)
  } else {
    genus <- NA
  }
  
  # Return rowname if genus is NA, empty, or 'uncultured'
  if (is.na(genus) || genus == "" || tolower(genus) == "uncultured") {
    return(rowname)
  } else {
    return(genus)
  }
}


get_X_selected <- function(condition){
  if (condition == "Drought") {
    Data <- readRDS(here("data/SoyData_Drought2.RDS"))
  } else if (condition == "Control") {
    Data <- readRDS(here("data/SoyData_Control2.RDS"))
  } else {
    stop("Unknown condition")
  }

  genome <- scale(Data$genome)
  met.cd <- scale(Data$met)
  mic.cd <- scale(Data$mic)
  X_all <- cbind(genome, mic.cd, met.cd)

  # imp_common_cols に基づいて選択
  selected_columns <- intersect(imp_common_cols, colnames(X_all))
  X_selected <- X_all[, selected_columns, drop = FALSE]
  return(X_selected)
}
get_label <- function(name) {
  if (str_starts(name, "X")) {
    idx <- suppressWarnings(as.numeric(str_remove(name, "X")))
    if (!is.na(idx) && idx %in% 1:nrow(mm)) {
      out_label <- mm[idx, 1]
    } else {
      out_label <- NA
    }
  } else if (str_starts(name, "B")) {
    idx <- suppressWarnings(as.numeric(str_remove(name, "B")))
    if (!is.na(idx) && idx %in% 1:length(micro_labels_genus)) {
      out_label <- micro_labels_genus[idx]
    } else {
      out_label <- NA
    }
  } else {
    out_label <- name
  }

  if (!is.na(out_label)) {
    out_label <- substr(out_label, 1, 60)
  }

  return(out_label)
}



```


```{r}
# 1. 両方の重要度ファイルを読み込み
imp_drought <- readRDS(here("out", "imp_RF2_d.RDS"))
imp_control <- readRDS(here("out", "imp_RF2_c.RDS"))


# 2. 各条件で重要度の高い列を抽出（しきい値 0.01）
imp_d_cols <- colnames(imp_drought)[colSums(imp_drought) >= 0.01]
imp_c_cols <- colnames(imp_control)[colSums(imp_control) >= 0.01]

# 3.カバーする重要な特徴量
imp_common_cols <- union(imp_d_cols, imp_c_cols)

# 4. 各条件で X_selected を作成
X_selected_drought <- get_X_selected("Drought")
X_selected_control <- get_X_selected("Control")

# 5. 最終的に両者に共通する列名だけを残す
common_features <- intersect(colnames(X_selected_drought), colnames(X_selected_control))

X_selected_drought <- X_selected_drought[, common_features, drop = FALSE]
X_selected_control <- X_selected_control[, common_features, drop = FALSE]

# 結果表示
cat("共通する特徴量の数:", length(common_features), "\n")
cat("X_selected_drought の次元:", dim(X_selected_drought), "\n")
cat("X_selected_control の次元:", dim(X_selected_control), "\n")
```


```{r}
all_sums <- c(colSums(imp_drought), colSums(imp_control))
range_all <- range(all_sums)

range_all<-c(0,0.02)
# 同じ breaks と xlim を使って比較
hist(colSums(imp_drought), 
      main = expression("RF Importance (" * i[k] * ") - Drought"),
		 #sub = "(sum across all biomass phenotypes)",
     xlim = range_all, 
		 ylim = c(0,5000),
     breaks = 100, 
     col = rgb(1, 0, 0, 0.5),
		 ylab = "Number of features",
     xlab = expression("Sum of importance values across phenotypes (" * i[k] * ")"))

hist(colSums(imp_control), 
      main = expression("RF Importance (" * i[k] * ") - Control"),
		 #sub = "(sum across all biomass phenotypes)",
     xlim = range_all, 
		 ylim = c(0,5000),
     breaks = 100, 
     col = rgb(0, 0, 1, 0.5),
		 ylab = "Number of features",
     xlab = expression("Sum of importance values across phenotypes (" * i[k] * ")"))


```

# SHAP net
```{r}
set.seed(123)


cd2<- c("Control","Drought")
for (cd in cd2) {

# Combine and scale feature sets
#cd<-"Control" 
#cd<-"Drought" 

if (cd == "Drought") {
  X <- X_selected_drought
  Data <- readRDS(here("data/SoyData_Drought2.RDS"))
} else if (cd == "Control") {
  X <- X_selected_control
  Data <- readRDS(here("data/SoyData_Control2.RDS"))
} else {
  stop("Unknown condition")
}

genome<-Data$genome
grm.cd<-Data$grm
met.cd<-Data$met
mic.cd<-Data$mic

psc19<-Data$pheno
microname<-Data$microname
metname<-Data$metname
cd<-Data$cd

genome<- scale(genome)
met.cd<-scale(met.cd)
mic.cd <- scale(mic.cd)
psc19 <- scale(psc19)


mm<-matrix(metname,length(metname),1)
rownames(mm)<-  paste0("X", 1:length(metname))

cm<-matrix(microname,length(microname),1)
rownames(cm)<-  paste0("B", 1:length(microname))

mm <- gsub(
  pattern = "^(DL-|L-\\(-\\)|D-\\(-\\)|L-|D-|(+-)-|(-)-)|(+-)-|D-", 
  replacement = "", 
  x = mm
)


mm[182]<-"Marein"
mm[187]<-"Sodium pantothenate"
mm[189]<-"Mannose-6-phosphate"
mm[190]<-"Fructose-6-phosphate"
mm[197]<-"Mannitol"
mm[208]<-"Indole-3-carboxyaldehyde"
mm[53]<-"Ornithine"
mm[75]<-"GABA"
mm[38] <-"2,3-Diaminopropionic acid"
mm[102]<-"Quinic acid"
mm[227]<-"Quercetin 3-Glucoside"
mm[205]<-"Threonine"
mm[206]<-"2-Aminobutyric acid"
mm[188]<- "Glucose-1-phosphate"

micro_labels_genus <- mapply(extract_genus, cm[,1], rownames(cm))


dim(X)
X <- scale(X)
X <- data.frame(X)

# Load target variable (phenotype)
Y <- data.frame(psc19)

#X<-X[c(1:3),]
#Y<-Y[c(1:3),]

# Check dimensions (optional)
dim(X)
dim(Y)

# Initialize list to store SHAP results
shap_all <- list()

# Loop over phenotype(s), here using only the first one for simplicity
for (i in 1) {
  cat("Processing phenotype:", colnames(Y)[i], "\n")

  # Create a new dataframe that includes the response variable
  df <- X
  df[[colnames(Y)[i]]] <- Y[[i]]

  # Train a random forest model using ranger
  rf_model <- ranger(
    formula = as.formula(paste(colnames(Y)[i], "~ .")),
    data = df
    #,num.trees = 100
  )

  # Create an iml Predictor object
  predictor <- Predictor$new(rf_model, data = X, y = Y[[i]])

  # Add a progress bar to track SHAP computation
  pb <- progress_bar$new(
    format = "  SHAP calculation [:bar] :percent in :elapsed",
    total = nrow(X), clear = FALSE, width = 60
  )

  # Compute SHAP values for each sample
  shap_all_results <- lapply(1:nrow(X), function(j) {
  #shap_all_results <- lapply(1:4, function(j) {
    pb$tick()
    shap <- Shapley$new(predictor, x.interest = X[j, , drop = FALSE])
    shap$results
  })

  # Combine SHAP results into a single dataframe
  shap_df <- do.call(rbind, shap_all_results)
  colnames(shap_df) <- c("feature", "phi", "feature_value")

  # Save SHAP results
  shap_all[[colnames(Y)[i]]] <- shap_df
}

# Extract SHAP results for the first phenotype
shap_df <- shap_all[[colnames(Y)[1]]]
shap_df <- shap_df[, !is.na(colnames(shap_df))]

#saveRDS(shap_df,here("out",paste0("shap_df",cd,"_def.rds")))

}
```



```{r}

node_colors <- c("Genome" = "#FF6F61",
                 "Microbiome" = "#66B032",
                 "Metabolome" = "orange",
                 "Phenotype" = "#9B4F96",
                 "Other" = "#B0B0B0")

# Load SHAP data for each condition
shap_df_control <- readRDS(here("out", "shap_dfControl_def.rds"))
shap_df_drought <- readRDS(here("out", "shap_dfDrought_def.rds"))

get_shap_summary <- function(shap_df, condition_name) {
  shap_df %>%
    group_by(feature) %>%
    summarise(mean_phi = mean(abs(phi)), .groups = "drop") %>%
    mutate(condition = condition_name)
}

shap_control <- get_shap_summary(shap_df_control, "Control")
shap_drought <- get_shap_summary(shap_df_drought, "Drought")
add_group_and_label <- function(df) {
  df %>%
    mutate(
      group = case_when(
        str_starts(feature, "C") ~ "Genome",
        str_starts(feature, "B") ~ "Microbiome",
        str_starts(feature, "X") ~ "Metabolome",
        TRUE ~ "Other"
      ),
      label = sapply(feature, get_label)
    ) %>%
    filter(!is.na(label))
}

shap_control <- add_group_and_label(shap_control)
shap_drought <- add_group_and_label(shap_drought)

###
shap_top_control <- shap_control %>% top_n(20, mean_phi)
# 
# ggplot(shap_top_control, aes(x = reorder(label, mean_phi), y = mean_phi, fill = group)) +
#   geom_col() +
#   coord_flip() +
#   scale_fill_manual(values = node_colors) +
#   labs(
#     title = "Top 20 SHAP Values – Control",
#     x = "Feature",
#     y = "Mean Absolute SHAP Value",
#     fill = "Feature Group"
#   ) +
#   theme_minimal()

shap_top_drought <- shap_drought %>% top_n(20, mean_phi)

# ggplot(shap_top_drought, aes(x = reorder(label, mean_phi), y = mean_phi, fill = group)) +
#   geom_col() +
#   coord_flip() +
#   scale_fill_manual(values = node_colors) +
#   labs(
#     title = "Top 20 SHAP Values – Drought",
#     x = "Feature",
#     y = "Mean Absolute SHAP Value",
#     fill = "Feature Group"
#   ) +
#   theme_minimal()


```



```{r,fig.height=5,fig.width=15}
library(patchwork)


p1 <- ggplot(shap_top_control, aes(x = reorder(label, mean_phi), y = mean_phi, fill = group)) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = node_colors) +
  scale_y_continuous(limits = c(0, 0.05), expand = c(0, 0)) +
  labs(
    title = "Top 20 SHAP Values – Control",
    x = "Feature",
    y = "Mean Absolute SHAP Value",
    fill = "Feature Group"
  ) +
  theme_minimal() +
  theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))

p2 <- ggplot(shap_top_drought, aes(x = reorder(label, mean_phi), y = mean_phi, fill = group)) +
  geom_col() +
  coord_flip() +
  scale_fill_manual(values = node_colors) +
  scale_y_continuous(limits = c(0, 0.05), expand = c(0, 0)) +
  labs(
    title = "Top 20 SHAP Values – Drought",
    x = "Feature",
    y = "Mean Absolute SHAP Value",
    fill = "Feature Group"
  ) +
  theme_minimal() +
  theme(plot.margin = unit(c(1, 1, 1, 1), "cm"))

# 並べる
p2 + p1

```


```{r,fig.width=9}

shap_ratio <- full_join(
  shap_control %>% select(feature, mean_phi_control = mean_phi),
  shap_drought %>% select(feature, mean_phi_drought = mean_phi),
  by = "feature"
) %>%
  mutate(
    ratio = mean_phi_drought / mean_phi_control,
    log2_ratio = log2(ratio),
    label = sapply(feature, get_label),
    group = case_when(
      str_starts(feature, "C") ~ "Genome",
      str_starts(feature, "B") ~ "Microbiome",
      str_starts(feature, "X") ~ "Metabolome",
      TRUE ~ "Other"
    )
  ) %>%
  filter(!is.na(ratio), is.finite(ratio), !is.na(label))


#```{r}
# Top 10 Up and Down
shap_ratio_up <- shap_ratio %>%
  filter(log2_ratio > 2.5) %>%
  arrange(desc(log2_ratio)) %>%
  slice_head(n = 20)

shap_ratio_down <- shap_ratio %>%
  filter(log2_ratio < -2.5) %>%
  arrange(log2_ratio) %>%
  slice_head(n = 20)



#Combine both
shap_ratio_combined <- bind_rows(shap_ratio_up, shap_ratio_down)

shap_ratio_combined$label[shap_ratio_combined$label == "B113"] <- "Uncultured (Methylophilaceae)"
shap_ratio_combined$label[shap_ratio_combined$label == "B356"] <- "Uncultured (Comamonadaceae)"


# Plot
ggplot(shap_ratio_combined, aes(x = reorder(label, log2_ratio), y = log2(ratio), fill = group)) +
  geom_col() +
	#geom_hline(yintercept = 2, linetype = "dashed", color = "gray50") +
	#geom_hline(yintercept = -2, linetype = "dashed", color = "gray50") +
  coord_flip() +
  #geom_hline(yintercept = 0, linetype = "dashed", color = "gray40") +
  scale_fill_manual(values = node_colors) +
  labs(
    title = "Selected features by SHAP value (Drought / Control)",
    x = "Feature",
    y = "log2( mean absolute SHAP Ratio: Drought / Control)",
    fill = "Feature Group"
  ) +
	#scale_y_continuous(breaks = seq(-6, 6, by = 1)) + 
  theme_minimal() +
theme(
  axis.text.y = element_text(size = 12),
  axis.text.x = element_text(size = 12),
  plot.title = element_text(size = 14, face = "bold")
)


```


