
```{r, include = FALSE}
knitr::opts_chunk$set(eval = TRUE)
```

seed
```{r, message =F, include=FALSE}
# save or read the seed
seedIndCsv <-  here("out","seedInd.csv")
if (file.exists(seedIndCsv)) {
  seedInd <- read.csv(seedIndCsv, row.names = 1, header = T)
  seedInd <- c(as.matrix(seedInd))
} else {
  seedInd <- sample(1:500, 10, replace = F)
  write.csv(x = seedInd, file =  here("out","seedInd.csv"))
}
```

## 3.1 Model Build for 2020 Yield Prediction
Oneout 47 ver2
For the inter-year prediction problem, we set the following prediction rules (PR).   
- the PR based on Genetic information only, ie the classical GBLUP    
- the PR based on Genetic and Micro  
- the PR based on Genetic, Micro and Meta  
- the PR based on Genetic, Micro and predicted Meta based on Genetic and Micro  


required packages
```{r, message =F}
require(BGLR)
require(here)
require(ggplot2)
require(reshape2)
require(gridExtra)
library(readr)
library(stringr)
library(ggsci)
library(RAINBOWR)
library(lubridate)
library(foreach)
library(future)
library(doFuture)
library(doRNG)
library(doSNOW)
```

read phenotypic data
```{r}
pheno18 <- read.csv(here("2018", "shoot_blup_all_2018.csv"), row.names = 1)
pheno19 <- read.csv(here("2019", "shoot_blup_all_2019.csv"), row.names = 1)
pheno20 <- read.csv(here("2020", "shoot_blup_all_2020.csv"), row.names = 1)

plot18<-rownames(pheno18)
plot19<-rownames(pheno19)
plot20<-rownames(pheno20)

var18<-pheno18$var.id
var19<-pheno19$var.id
var20<-pheno20$var.id
```

read genomic relationship matrix data
```{r}
grm <- readRDS(here("data", "grm_2.rds"))
head(grm)[,1:3]
```

read metabolomic data
```{r}
met<- read.csv(here("2019","2019_Tottori_Jul_RootMetabolome_X.csv"))
rownames(met) <- paste0(substr(as.matrix(met[7]),1,2),".",sprintf("%03d",as.matrix(met[8])))
met19 <- met[,10:ncol(met)]
colnames(met19)<- sub("M","X",colnames(met19))

met <- read.csv(here("2020", "2020_Tottori_Main_RootMetabolome.csv"))
rownames(met) <- paste0(substr(as.matrix(met[7]),1,2),".",sprintf("%03d",as.matrix(met[8])))
met20 <- met[,10:ncol(met)]

s_c <- colnames(met19) %in% colnames(met20)
met19<- met19[,s_c]
s_c <- colnames(met20) %in% colnames(met19)
met20<- met20[,s_c]
table(colnames(met20) == colnames(met19))

dim(met19)
dim(met20)
```



read microbiome rarificated data
```{r}
com <- read.table(here("2018", "table-from-biom-7-2018-after.txt"), row.names = 1)
rownames(com) <- gsub(";",".",rownames(com))
com18<- com
colnames(com18) <- cbind(plot18[201:400],plot18[601:800])

com <- read.csv(here("2019", "table-from-biom-7.csv"), row.names = 1)
rownames(com) <- gsub(";",".",rownames(com))
com19<- com

#comriken <- read.csv(here("2020", "table-from-biom-7-2020-after.csv"))
com <- read.csv(here("2020", "2020_Tottori_Main_Microbiome_Ratio.csv"))
rownames(com) <- paste0(substr(as.matrix(com[7]),1,2),".",sprintf("%03d",as.matrix(com[8])))
com <- com[,10:ncol(com)]
com20 <- t(com)

#s_c <- rownames(com19) %in% rownames(com20)
#com19<- com19[s_c,]
#s_c <- rownames(com20) %in% rownames(com19)
#com20<- com20[s_c,]

s_c <- (rownames(com19) %in% rownames(com20)) & (rownames(com19) %in% rownames(com18))
com19<- com19[s_c,]
s_c <- rownames(com20) %in% rownames(com19)
com20<- com20[s_c,]
s_c <- rownames(com18) %in% rownames(com20)
com18<- com18[s_c,]

dim(com18)
dim(com19)
dim(com20)
```


### Drought

```{r}
CD ="W4"
```

read predmet
```{r}
predmet20f19 <- read.csv(here("out", "20f19_predmet_GM_blup_OneOut.csv"), row.names = 1)
predmet19f20 <- read.csv(here("out", "19f20_predmet_GM_blup_OneOut.csv"), row.names = 1)

predmet19 <- read.csv(here("out", "19f19_predmet_GM_blup_OneOut.csv"), row.names = 1)
predmet20 <- read.csv(here("out", "20f20_predmet_GM_blup_OneOut.csv"), row.names = 1)

predmet_sel19 <- read.csv(here("out", "19f19_predmet_GM_blup_OneOut_cor0.csv"), row.names = 1)
predmet_sel20 <- read.csv(here("out", "20f20_predmet_GM_blup_OneOut_cor0.csv"), row.names = 1)

```

select the lines which has pheno, grm, met, micro data in 2019 and 2020
```{r}
selector.grm1 <- pheno18$var.id %in% rownames(grm)
selector.com1 <-rownames(pheno18) %in% colnames(com18)

selector.grm2 <- pheno19$var.id %in% rownames(grm)
selector.com2 <-rownames(pheno19) %in% colnames(com19)

selector.grm3 <- pheno20$var.id %in% rownames(grm)
selector.com3 <-rownames(pheno20) %in% colnames(com20)


pl<- list(pheno18,pheno19,pheno20)
pl.sel<- list()

for (i in 2:3){
pheno<- pl[[i]]

if (i==1) {
  selector.grm <- selector.grm1
  selector.com <- selector.com1
}

else if (i==2) {
  selector.grm <- selector.grm2
  selector.com <- selector.com2
}

else if (i==3) {
  selector.grm <- selector.grm3
  selector.com <- selector.com3
}


pheno.sel <- pheno[selector.grm & selector.com, ]
#head(pheno.sel)
print(dim(pheno.sel))

selector.cd <- substr(rownames(pheno.sel), 1, 2) == CD 
pheno.sel.cd <- pheno.sel[selector.cd, ]
dim(pheno.sel.cd)

plot.id <- rownames(pheno.sel.cd)
rownames(pheno.sel.cd)<-pheno.sel.cd$var.id
pheno.sel.cd$var.id <- plot.id
colnames(pheno.sel.cd)[1]<- "plot.id"
sg <- rownames(grm) %in% rownames(pheno.sel.cd)
gv<-rownames(grm[sg,sg])
pheno.sel.cd<- pheno.sel.cd[gv,]
print(dim(pheno.sel.cd))
pl.sel[[i]]<- pheno.sel.cd
}

#psc18<-  pl.sel[[1]]
psc19<-  pl.sel[[2]] 
psc20<-  pl.sel[[3]]



s_p <- rownames(psc19) %in% rownames(psc20)
psc19<- psc19[s_p,]
s_p <- rownames(psc20) %in% rownames(psc19)
psc20<- psc20[s_p,]

s_p <- colnames(psc19) %in% colnames(psc20)
psc19<- psc19[,s_p]
s_p <- colnames(psc20) %in% colnames(psc19)
psc20<- psc20[,s_p]

table(rownames(psc19) == rownames(psc20))

```



2019 
```{r}
var.id <- rownames(psc19)
grm.cd <- grm[var.id, var.id]
plot.id  <- psc19$plot.id
com19.cd <- t(com19[, plot.id])
com19.cd <- scale(com19.cd[, apply(com19.cd, 2, sd) > 0])
#met19ns.cd <- met19[plot.id, ]
met19.cd <- scale(met19[plot.id, ])
#predmet19ns<-predmet19
predmet19<-scale(predmet19)
```


2020
```{r, message =F}
var.id <- rownames(psc20)
grm.cd <- grm[var.id, var.id]
plot.id  <- psc20$plot.id
com20.cd <- t(com20[, plot.id])
com20.cd <- scale(com20.cd[, apply(com20.cd, 2, sd) > 0])
#met20ns.cd <- met20[plot.id, ]
met20.cd <- scale(met20[plot.id, ])
#predmetns20<-predmet20
predmet20<-scale(predmet20)
#predmetns20f19<-predmet20f19
predmet20f19<-scale(predmet20f19)
predmet19f20<-scale(predmet19f20)
```


Integrate + RM
```{r, message =F}
psc <- rbind(psc19,psc20)

s_c <- colnames(com19.cd) %in% colnames(com20.cd)
com19.cd<- com19.cd[,s_c]
s_c <- colnames(com20.cd) %in% colnames(com19.cd)
com20.cd<- com20.cd[,s_c]

s_c <- colnames(com19.cd) %in% colnames(com20.cd)
com19.cd<- com19.cd[,s_c]
s_c <- colnames(com20.cd) %in% colnames(com19.cd)
com20.cd<- com20.cd[,s_c]

mrm19.cd <- tcrossprod(com19.cd) / ncol(com19.cd)
mrm20.cd <- tcrossprod(com20.cd) / ncol(com20.cd)

com.cd<- rbind(com19.cd,com20.cd)
rownames(com.cd)<-rownames(psc)
mrm.cd <- tcrossprod(com.cd) / ncol(com.cd)

metrm19.cd <- tcrossprod(met19.cd) / ncol(met19.cd)
metrm20.cd <- tcrossprod(met20.cd) / ncol(met20.cd)

metPrm19.cd <- tcrossprod(predmet19) / ncol(predmet19)
metPrm20.cd <- tcrossprod(predmet20) / ncol(predmet20)

metPrm20f19.cd <- tcrossprod(predmet20f19) / ncol(predmet20f19)
metPrm19f20.cd <- tcrossprod(predmet19f20) / ncol(predmet19f20)

#metns.cd <- rbind(met19ns.cd,met20ns.cd)
met.cd<- rbind(met19.cd,met20.cd)
rownames(met.cd)<-rownames(psc)
metrm.cd <- tcrossprod(met.cd) / ncol(met.cd)
```


### 2020model
```{r, message =F}
K1 <- grm.cd
K2 <- mrm20.cd
K3 <- metrm20.cd
K8 <- metPrm20f19.cd
K9 <- metPrm20.cd

Z <- design.Z(pheno.labels = rownames(grm.cd),geno.names = rownames(grm.cd))

KZ1<- list(A= list(K = K1, Z = Z))
KZ2<- list(A= list(K = K2, Z = Z))
KZ3<- list(A= list(K = K3, Z = Z))
KZ8<- list(A= list(K = K8, Z = Z))
KZ9<- list(A= list(K = K9, Z = Z))

KZ12<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z))

KZ128<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K8, Z = Z))
KZ129<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K9, Z = Z))
KZ123<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K3, Z = Z))

ZETAlist <- list(KZ1,KZ2,KZ8,KZ9,KZ3,KZ12,KZ128,KZ129,KZ123)
names(ZETAlist) <- c("KZ1","KZ2","KZ8","KZ9","KZ3","KZ12","KZ128","KZ129","KZ123")
names<- names(ZETAlist)

```


ModelRun
```{R, message =F, include=TRUE,eval=TRUE}
y <- psc20

resultModelname <- names(ZETAlist)

doFuture::registerDoFuture()
plan("multisession", workers = 6)

xr <- foreach(zl = ZETAlist) %dopar% {

  zname = names(zl)
  print(zname)
  
  var.pheno.all = c() #traitごと結果(要約)
  
  ZETA <- zl
  X0 <- NULL
  
  for (i in 2:ncol(y)){
  #for (i in 2){  
    trait.name <- colnames(y)[i]
    print(c(i,"/",ncol(y)))
    print(trait.name)
    # make the case for the result
    
    resultIndex <- c("Correlation", "R2", "RMSE","varU","varE","h2")
    resultEachSeed <- matrix(NA, ncol = length(resultIndex), nrow = length(seedInd))
    colnames(resultEachSeed) <- resultIndex
    rownames(resultEachSeed) <- seedInd
    
    predictionDataRAINBOW <- rep(NA, nrow(y))
    
    for (t in 1:nrow(y)) { 
    #for (t in 1:3) {
      yNa <- y[,i]
      yNa[t] <- NA
      # RAINBOWR
      resEM3 <- EM3.cpp(y = yNa,
                        X0 = X0, n.core = 1, 
                        ZETA = ZETA)
      # input the predicted data
      predictionDataRAINBOW[t] <- resEM3$y.pred[t]
    }
    
    # resEM3$weights
    predictData <- (predictionDataRAINBOW)
    obsData <- (y[,i])
    
    # calculate the R2 and RMSE
    correlation <- cor(obsData, predictData)
    R2 <- 1 - sum((obsData - predictData) ^ 2) / sum((obsData - mean(obsData)) ^ 2)
    RMSE <- sqrt(sum((obsData - predictData) ^ 2) / length(obsData))
    VU <- resEM3$Vu
    VE <- resEM3$Ve
    h2 <-  VU/(VU+VE)
    
    resultsum<- c(correlation, R2, RMSE,VU,VE,h2)
    resultsum<- as.matrix(resultsum)
    colnames(resultsum) <-trait.name
       var.pheno.all <- cbind(var.pheno.all,resultsum)
  }
  
  rownames(var.pheno.all) <- resultIndex
  print(var.pheno.all)
  var.pheno.all
}


resultModelname <- names(ZETAlist)
resultEachModel <- matrix(NA, nrow = length(ZETAlist), ncol = ncol(y)-1)
rownames(resultEachModel) <- names(ZETAlist)
colnames(resultEachModel) <- colnames(y)[2:ncol(y)]

#index p generator
for (n in 1:length(names)){
  
  resultEachModel[n,]<- xr[[n]][1,]
  
  if (n == 1){
    p <- names[1]
  }
  else{
    p  <- paste(p,names[n],sep="")
  }
}
print(p)


names(xr) <- names
resultEachModel_all<- xr


```

csv
```{R,eval=TRUE}
write.csv(resultEachModel, 
here("out",paste0("2020_blup",p,"_OneOut.csv" )))
#here("out",paste0("2020_blup",p,substr(now(),1,10),substr(now(),12,13),substr(now(),15,16),"_OneOut.csv" )))

write.csv(resultEachModel_all, here("out",paste0("2020_blup_ResAll_",p,"_OneOut.csv" )))
```


result plot
```{R,fig.dim = c(8, 4)}

#pred.all<-resultEachModel
p= "KZ1KZ2KZ8KZ9KZ3KZ12KZ128KZ129KZ123"
pred.all <- read.csv(here("out",paste0("2020_blup",p,"_OneOut.csv" )),row.names=1)

model.name <- c("G", "Micro", "PredMet_f19","PredMet_f20", "TrueMet", "G+Micro", "G+Micro+PredMet_f19","G+Micro+PredMet_f20","G+Micro+TrueMet")
trait.name <- colnames(pred.all)
df.all <- NULL

for(i in 1:length(trait.name)) {
  
  pred <-  pred.all[,i]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}


df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- colnames(pred.all)
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge")  + ggtitle("Yield Prediction in 2020")
print(g)
```

The results of the yield prediction in 2020.
PredMet_f19 represents Metabolome data predicted by 2019 dataset.  
When comparing G + Micro vs G + Micro + PredMet_f19, the accuracy is higher in G + Micro + PredMet_f19, which implies predicted met contributes to the yield prediction.    
The accuracy of one-year model was worse than inter-year. This may be due to outliers in the one-year Met prediction. We previously tried the Random Forest model for Met predictions for the one-year model and found fewer outliers; we need to consider which model to use for the one-year model to reduce the outliers.



###2019model

```{r, message =F, include=TRUE,eval=TRUE}
K1 <- grm.cd
K2 <- mrm19.cd
K3 <- metrm19.cd
K8 <- metPrm19.cd
K9 <- metPrm19f20.cd


Z <- design.Z(pheno.labels = rownames(grm.cd),geno.names = rownames(grm.cd))

KZ1<- list(A= list(K = K1, Z = Z))
KZ2<- list(A= list(K = K2, Z = Z))
KZ3<- list(A= list(K = K3, Z = Z))
KZ8<- list(A= list(K = K8, Z = Z))
KZ9<- list(A= list(K = K9, Z = Z))

KZ12<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z))

KZ128<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K8, Z = Z))
KZ129<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K9, Z = Z))
KZ123<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K3, Z = Z))

ZETAlist <- list(KZ1,KZ2,KZ8,KZ9,KZ3,KZ12,KZ128,KZ129,KZ123)
names(ZETAlist) <- c("KZ1","KZ2","KZ8","KZ9","KZ3","KZ12","KZ128","KZ129","KZ123")
names<- names(ZETAlist)

```


ModelRun
```{R, message =F, include=TRUE,eval=TRUE}
y <- psc19

resultModelname <- names(ZETAlist)

doFuture::registerDoFuture()
plan("multisession", workers = 6)

xr <- foreach(zl = ZETAlist) %dopar% {
#xr <- foreach(zl = ZETAlist) %dopar% {
  #for (zl in ZETAlist){
  #for (zl in ZETAlist[1]){
  zname = names(zl)
  print(zname)
  
  var.pheno.all = c() #traitごと結果(要約)
  
  ZETA <- zl
  X0 <- NULL
  
  for (i in 2:ncol(y)){
  #for (i in 2){  
    trait.name <- colnames(y)[i]
    print(c(i,"/",ncol(y)))
    print(trait.name)
    # make the case for the result
    
    resultIndex <- c("Correlation", "R2", "RMSE","varU","varE","h2")
    resultEachSeed <- matrix(NA, ncol = length(resultIndex), nrow = length(seedInd))
    colnames(resultEachSeed) <- resultIndex
    rownames(resultEachSeed) <- seedInd
    
    predictionDataRAINBOW <- rep(NA, nrow(y))
    
    for (t in 1:nrow(y)) { 
    #for (t in 1:3) {
      yNa <- y[,i]
      yNa[t] <- NA
      # RAINBOWR
      resEM3 <- EM3.cpp(y = yNa,
                        X0 = X0, n.core = 1, 
                        ZETA = ZETA)
      # input the predicted data
      predictionDataRAINBOW[t] <- resEM3$y.pred[t]
    }
    
    # resEM3$weights
    predictData <- (predictionDataRAINBOW)
    obsData <- (y[,i])
    
    # calculate the R2 and RMSE
    correlation <- cor(obsData, predictData)
    R2 <- 1 - sum((obsData - predictData) ^ 2) / sum((obsData - mean(obsData)) ^ 2)
    RMSE <- sqrt(sum((obsData - predictData) ^ 2) / length(obsData))
    VU <- resEM3$Vu
    VE <- resEM3$Ve
    h2 <-  VU/(VU+VE)
    
    resultsum<- c(correlation, R2, RMSE,VU,VE,h2)
    resultsum<- as.matrix(resultsum)
    colnames(resultsum) <-trait.name
       var.pheno.all <- cbind(var.pheno.all,resultsum)
  }
  
  rownames(var.pheno.all) <- resultIndex
  print(var.pheno.all)
  var.pheno.all
}


resultModelname <- names(ZETAlist)
resultEachModel <- matrix(NA, nrow = length(ZETAlist), ncol = ncol(y)-1)
rownames(resultEachModel) <- names(ZETAlist)
colnames(resultEachModel) <- colnames(y)[2:ncol(y)]

#index p generator
for (n in 1:length(names)){
  
  resultEachModel[n,]<- xr[[n]][1,]
  
  if (n == 1){
    p <- names[1]
  }
  else{
    p  <- paste(p,names[n],sep="")
  }
}
print(p)


names(xr) <- names
resultEachModel_all<- xr


```

csv
```{R,eval=TRUE}
write.csv(resultEachModel, here("out",paste0("2019_blup",p,"_OneOut.csv" )))

write.csv(resultEachModel_all, here("out",paste0("2019_blup_ResAll_",p,"_OneOut.csv" )))
```


result plot
```{R,fig.dim = c(8, 4)}

#pred.all<-resultEachModel
pred.all <- read.csv(here("out",paste0("2019_blup",p,"_OneOut.csv" )),row.names=1)

model.name <- c("G", "Micro", "PredMet_f19","PredMet_f20", "TrueMet", "G+Micro", "G+Micro+PredMet_f19","G+Micro+PredMet_f20","G+Micro+TrueMet")
trait.name <- colnames(pred.all)
df.all <- NULL

for(i in 1:length(trait.name)) {
  
  pred <-  pred.all[,i]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}


df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- colnames(pred.all)
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge")  + ggtitle("Yield Prediction in 2019")
print(g)
```


#### optimal True Met

```{r}
ZETAlist <- list(KZ8,KZ9,KZ128,KZ129)
names(ZETAlist) <- c("KZ8","KZ9","KZ128","KZ129")
names<- names(ZETAlist)
```


```{R, message =F, include=TRUE,eval=TRUE}
y <- psc19

resultModelname <- names(ZETAlist)

doFuture::registerDoFuture()
plan("multisession", workers = 4)

#zl = ZETAlist[[1]]
xr <- foreach(zl = ZETAlist) %dopar% {
  
  znum=1
  zname = names(ZETAlist)[znum]
  print(zname)
  znum = znum+1
  
  var.pheno.all = c() #traitごと結果(要約)
  
  ZETA <- zl
  
  X0 <- NULL
  
  for (i in 2:ncol(y)){
  #for (i in 2){  
    trait.name <- colnames(y)[i]
    print(c(i,"/",ncol(y)))
    print(trait.name)
    # make the case for the result
    
    resultIndex <- c("Correlation", "R2", "RMSE","varU","varE","h2")
    resultEachSeed <- matrix(NA, ncol = length(resultIndex), nrow = length(seedInd))
    colnames(resultEachSeed) <- resultIndex
    rownames(resultEachSeed) <- seedInd
    
    predictionDataRAINBOW <- rep(NA, nrow(y))
    
    for (t in 1:nrow(y)) { 
    #for (t in 1:3) {
      
      tf<- 1:nrow(y) == t
      
      if (zname == "KZ8" | zname == "KZ9"){
      ZETA[[1]][["K"]][!tf,] <- K3[!tf,]
      }
      
      if(zname == "KZ128" | zname == "KZ129"){
      ZETA[[3]][["K"]][!tf,]  <- K3[!tf,]
      }
      
      yNa <- y[,i]
      yNa[t] <- NA
      # RAINBOWR
      resEM3 <- EM3.cpp(y = yNa,
                        X0 = X0, n.core = 1, 
                        ZETA = ZETA)
      # input the predicted data
      predictionDataRAINBOW[t] <- resEM3$y.pred[t]
    }
    
    # resEM3$weights
    predictData <- (predictionDataRAINBOW)
    obsData <- (y[,i])
    
    # calculate the R2 and RMSE
    correlation <- cor(obsData, predictData)
    R2 <- 1 - sum((obsData - predictData) ^ 2) / sum((obsData - mean(obsData)) ^ 2)
    RMSE <- sqrt(sum((obsData - predictData) ^ 2) / length(obsData))
    VU <- resEM3$Vu
    VE <- resEM3$Ve
    h2 <-  VU/(VU+VE)
    
    resultsum<- c(correlation, R2, RMSE,VU,VE,h2)
    resultsum<- as.matrix(resultsum)
    colnames(resultsum) <-trait.name
       var.pheno.all <- cbind(var.pheno.all,resultsum)
  }
  
  rownames(var.pheno.all) <- resultIndex
  print(var.pheno.all)
  var.pheno.all
}


resultModelname <- names(ZETAlist)
resultEachModel <- matrix(NA, nrow = length(ZETAlist), ncol = ncol(y)-1)
rownames(resultEachModel) <- names(ZETAlist)
colnames(resultEachModel) <- colnames(y)[2:ncol(y)]

#index p generator
for (n in 1:length(names)){
  
  resultEachModel[n,]<- xr[[n]][1,]
  
  if (n == 1){
    p <- names[1]
  }
  else{
    p  <- paste(p,names[n],sep="")
  }
}
print(p)


names(xr) <- names
resultEachModel_all<- xr


```


csv
```{R,eval=TRUE}
write.csv(resultEachModel, here("out",paste0("2019_blup",p,"_OneOut_opt.csv" )))

write.csv(resultEachModel_all, here("out",paste0("2019_blup_ResAll_",p,"_OneOut_opt.csv" )))
```


###Control


```{r}
CD ="W1"
```

read predmet
```{r}
predmet20f19 <- read.csv(here("out", "20f19_predmet_GM_blup_OneOut_c.csv"), row.names = 1)
predmet19f20 <- read.csv(here("out", "19f20_predmet_GM_blup_OneOut_c.csv"), row.names = 1)

predmet19 <- read.csv(here("out", "19f19_predmet_GM_blup_OneOut_c.csv"), row.names = 1)
predmet20 <- read.csv(here("out", "20f20_predmet_GM_blup_OneOut_c.csv"), row.names = 1)

predmet_sel19 <- read.csv(here("out", "19f19_predmet_GM_blup_OneOut_cor0_c.csv"), row.names = 1)
predmet_sel20 <- read.csv(here("out", "20f20_predmet_GM_blup_OneOut_cor0_c.csv"), row.names = 1)

```


select the lines which has pheno, grm, met, micro data in 2019 and 2020
```{r}
selector.grm1 <- pheno18$var.id %in% rownames(grm)
selector.com1 <-rownames(pheno18) %in% colnames(com18)

selector.grm2 <- pheno19$var.id %in% rownames(grm)
selector.com2 <-rownames(pheno19) %in% colnames(com19)

selector.grm3 <- pheno20$var.id %in% rownames(grm)
selector.com3 <-rownames(pheno20) %in% colnames(com20)


pl<- list(pheno18,pheno19,pheno20)
pl.sel<- list()

for (i in 2:3){
pheno<- pl[[i]]

if (i==1) {
  selector.grm <- selector.grm1
  selector.com <- selector.com1
}

else if (i==2) {
  selector.grm <- selector.grm2
  selector.com <- selector.com2
}

else if (i==3) {
  selector.grm <- selector.grm3
  selector.com <- selector.com3
}


pheno.sel <- pheno[selector.grm & selector.com, ]
#head(pheno.sel)
print(dim(pheno.sel))

selector.cd <- substr(rownames(pheno.sel), 1, 2) == CD 
pheno.sel.cd <- pheno.sel[selector.cd, ]
dim(pheno.sel.cd)

plot.id <- rownames(pheno.sel.cd)
rownames(pheno.sel.cd)<-pheno.sel.cd$var.id
pheno.sel.cd$var.id <- plot.id
colnames(pheno.sel.cd)[1]<- "plot.id"
sg <- rownames(grm) %in% rownames(pheno.sel.cd)
gv<-rownames(grm[sg,sg])
pheno.sel.cd<- pheno.sel.cd[gv,]
print(dim(pheno.sel.cd))
pl.sel[[i]]<- pheno.sel.cd
}

#psc18<-  pl.sel[[1]]
psc19<-  pl.sel[[2]] 
psc20<-  pl.sel[[3]]



s_p <- rownames(psc19) %in% rownames(psc20)
psc19<- psc19[s_p,]
s_p <- rownames(psc20) %in% rownames(psc19)
psc20<- psc20[s_p,]

s_p <- colnames(psc19) %in% colnames(psc20)
psc19<- psc19[,s_p]
s_p <- colnames(psc20) %in% colnames(psc19)
psc20<- psc20[,s_p]

table(rownames(psc19) == rownames(psc20))

```



2019 
```{r}
var.id <- rownames(psc19)
grm.cd <- grm[var.id, var.id]
plot.id  <- psc19$plot.id
com19.cd <- t(com19[, plot.id])
com19.cd <- scale(com19.cd[, apply(com19.cd, 2, sd) > 0])
#met19ns.cd <- met19[plot.id, ]
met19.cd <- scale(met19[plot.id, ])
#predmet19ns<-predmet19
predmet19<-scale(predmet19)
```


2020
```{r, message =F}
var.id <- rownames(psc20)
grm.cd <- grm[var.id, var.id]
plot.id  <- psc20$plot.id
com20.cd <- t(com20[, plot.id])
com20.cd <- scale(com20.cd[, apply(com20.cd, 2, sd) > 0])
#met20ns.cd <- met20[plot.id, ]
met20.cd <- scale(met20[plot.id, ])
#predmetns20<-predmet20
predmet20<-scale(predmet20)
#predmetns20f19<-predmet20f19
predmet20f19<-scale(predmet20f19)
predmet19f20<-scale(predmet19f20)
```


Integrate + RM
```{r, message =F}
psc <- rbind(psc19,psc20)

s_c <- colnames(com19.cd) %in% colnames(com20.cd)
com19.cd<- com19.cd[,s_c]
s_c <- colnames(com20.cd) %in% colnames(com19.cd)
com20.cd<- com20.cd[,s_c]

s_c <- colnames(com19.cd) %in% colnames(com20.cd)
com19.cd<- com19.cd[,s_c]
s_c <- colnames(com20.cd) %in% colnames(com19.cd)
com20.cd<- com20.cd[,s_c]

mrm19.cd <- tcrossprod(com19.cd) / ncol(com19.cd)
mrm20.cd <- tcrossprod(com20.cd) / ncol(com20.cd)

com.cd<- rbind(com19.cd,com20.cd)
rownames(com.cd)<-rownames(psc)
mrm.cd <- tcrossprod(com.cd) / ncol(com.cd)

metrm19.cd <- tcrossprod(met19.cd) / ncol(met19.cd)
metrm20.cd <- tcrossprod(met20.cd) / ncol(met20.cd)

metPrm19.cd <- tcrossprod(predmet19) / ncol(predmet19)
metPrm20.cd <- tcrossprod(predmet20) / ncol(predmet20)

metPrm20f19.cd <- tcrossprod(predmet20f19) / ncol(predmet20f19)
metPrm19f20.cd <- tcrossprod(predmet19f20) / ncol(predmet19f20)

#metns.cd <- rbind(met19ns.cd,met20ns.cd)
met.cd<- rbind(met19.cd,met20.cd)
rownames(met.cd)<-rownames(psc)
metrm.cd <- tcrossprod(met.cd) / ncol(met.cd)
```


### 2020model
```{r, message =F}
K1 <- grm.cd
K2 <- mrm20.cd
K3 <- metrm20.cd
K8 <- metPrm20f19.cd
K9 <- metPrm20.cd

Z <- design.Z(pheno.labels = rownames(grm.cd),geno.names = rownames(grm.cd))

KZ1<- list(A= list(K = K1, Z = Z))
KZ2<- list(A= list(K = K2, Z = Z))
KZ3<- list(A= list(K = K3, Z = Z))
KZ8<- list(A= list(K = K8, Z = Z))
KZ9<- list(A= list(K = K9, Z = Z))

KZ12<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z))

KZ128<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K8, Z = Z))
KZ129<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K9, Z = Z))
KZ123<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K3, Z = Z))

ZETAlist <- list(KZ1,KZ2,KZ8,KZ9,KZ3,KZ12,KZ128,KZ129,KZ123)
names(ZETAlist) <- c("KZ1","KZ2","KZ8","KZ9","KZ3","KZ12","KZ128","KZ129","KZ123")
names<- names(ZETAlist)

```



ModelRun
```{R, message =F, include=TRUE,eval=TRUE}
y <- psc20

resultModelname <- names(ZETAlist)

doFuture::registerDoFuture()
plan("multisession", workers = 6)

xr <- foreach(zl = ZETAlist) %dopar% {
#xr <- foreach(zl = ZETAlist) %dopar% {
  #for (zl in ZETAlist){
  #for (zl in ZETAlist[1]){
  zname = names(zl)
  print(zname)
  
  var.pheno.all = c() #traitごと結果(要約)
  
  ZETA <- zl
  X0 <- NULL
  
  for (i in 2:ncol(y)){
  #for (i in 2){  
    trait.name <- colnames(y)[i]
    print(c(i,"/",ncol(y)))
    print(trait.name)
    # make the case for the result
    
    resultIndex <- c("Correlation", "R2", "RMSE","varU","varE","h2")
    resultEachSeed <- matrix(NA, ncol = length(resultIndex), nrow = length(seedInd))
    colnames(resultEachSeed) <- resultIndex
    rownames(resultEachSeed) <- seedInd
    
    predictionDataRAINBOW <- rep(NA, nrow(y))
    
    for (t in 1:nrow(y)) { 
    #for (t in 1:3) {
      yNa <- y[,i]
      yNa[t] <- NA
      # RAINBOWR
      resEM3 <- EM3.cpp(y = yNa,
                        X0 = X0, n.core = 1, 
                        ZETA = ZETA)
      # input the predicted data
      predictionDataRAINBOW[t] <- resEM3$y.pred[t]
    }
    
    # resEM3$weights
    predictData <- (predictionDataRAINBOW)
    obsData <- (y[,i])
    
    # calculate the R2 and RMSE
    correlation <- cor(obsData, predictData)
    R2 <- 1 - sum((obsData - predictData) ^ 2) / sum((obsData - mean(obsData)) ^ 2)
    RMSE <- sqrt(sum((obsData - predictData) ^ 2) / length(obsData))
    VU <- resEM3$Vu
    VE <- resEM3$Ve
    h2 <-  VU/(VU+VE)
    
    resultsum<- c(correlation, R2, RMSE,VU,VE,h2)
    resultsum<- as.matrix(resultsum)
    colnames(resultsum) <-trait.name
       var.pheno.all <- cbind(var.pheno.all,resultsum)
  }
  
  rownames(var.pheno.all) <- resultIndex
  print(var.pheno.all)
  var.pheno.all
}


resultModelname <- names(ZETAlist)
resultEachModel <- matrix(NA, nrow = length(ZETAlist), ncol = ncol(y)-1)
rownames(resultEachModel) <- names(ZETAlist)
colnames(resultEachModel) <- colnames(y)[2:ncol(y)]

#index p generator
for (n in 1:length(names)){
  
  resultEachModel[n,]<- xr[[n]][1,]
  
  if (n == 1){
    p <- names[1]
  }
  else{
    p  <- paste(p,names[n],sep="")
  }
}
print(p)


names(xr) <- names
resultEachModel_all<- xr


```


csv
```{R,eval=TRUE}
write.csv(resultEachModel, here("out",paste0("2020_blup",p,"_OneOut_c.csv" )))

write.csv(resultEachModel_all, here("out",paste0("2020_blup_ResAll_",p,"_OneOut_c.csv" )))
```

result plot
```{R,fig.dim = c(8, 4)}

pred.all<-resultEachModel
#red.all <- read.csv(here("out",paste0("2020_blup",p,"_OneOut_c.csv" )),row.names=1)

model.name <- c("G", "Micro", "PredMet_f19","PredMet_f20", "TrueMet", "G+Micro", "G+Micro+PredMet_f19","G+Micro+PredMet_f20","G+Micro+TrueMet")
trait.name <- colnames(pred.all)
df.all <- NULL

for(i in 1:length(trait.name)) {
  
  pred <-  pred.all[,i]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}


df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- colnames(pred.all)
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge")  + ggtitle("Yield Prediction in 2020")
print(g)
```


###2019model

```{r, message =F, include=TRUE,eval=TRUE}
K1 <- grm.cd
K2 <- mrm19.cd
K3 <- metrm19.cd
K8 <- metPrm19.cd
K9 <- metPrm19f20.cd


Z <- design.Z(pheno.labels = rownames(grm.cd),geno.names = rownames(grm.cd))

KZ1<- list(A= list(K = K1, Z = Z))
KZ2<- list(A= list(K = K2, Z = Z))
KZ3<- list(A= list(K = K3, Z = Z))
KZ8<- list(A= list(K = K8, Z = Z))
KZ9<- list(A= list(K = K9, Z = Z))

KZ12<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z))

KZ128<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K8, Z = Z))
KZ129<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K9, Z = Z))
KZ123<- list(A= list(K = K1, Z = Z),B= list(K = K2, Z = Z),C= list(K = K3, Z = Z))

ZETAlist <- list(KZ1,KZ2,KZ8,KZ9,KZ3,KZ12,KZ128,KZ129,KZ123)
names(ZETAlist) <- c("KZ1","KZ2","KZ8","KZ9","KZ3","KZ12","KZ128","KZ129","KZ123")
names<- names(ZETAlist)

```


ModelRun
```{R, message =F, include=TRUE,eval=TRUE}
y <- psc19

tic()
xr<- foreach(zl = ZETAlist,.export = "EM3.cpp") %do% {
  
  zname = names(zl)
  var.pheno.all = c() #traitごと結果(要約)
  
  ZETA <- zl
  X0 <- NULL
  
  resultModelname <- names
  
  iterations=ncol(y)-1
  
  cl <- makeCluster(10)
  registerDoSNOW(cl)
  pb <- txtProgressBar(max = iterations, style = 3)
  progress <- function(n) setTxtProgressBar(pb, n)
  opts <- list(progress = progress)
  
  
  res <- foreach(i = 2:ncol(y),.combine = "cbind",.options.snow = opts,.export = "EM3.cpp") %dopar% {
  #for (i in 2){  
    # make the case for the result
    trait.name <- colnames(y)[i]
    
    resultIndex <- c("Correlation", "R2", "RMSE","varU","varE","h2")
    resultEachSeed <- matrix(NA, ncol = length(resultIndex), nrow = length(seedInd))
    colnames(resultEachSeed) <- resultIndex
    rownames(resultEachSeed) <- seedInd
    
    predictionDataRAINBOW <- rep(NA, nrow(y))
    
    for (t in 1:nrow(y)) { 
    #for (t in 1) {
      yNa <- y[,i]
      yNa[t] <- NA
      # RAINBOWR
      resEM3 <- EM3.cpp(y = yNa,
                        X0 = X0, n.core = 1, 
                        ZETA = ZETA)
      # input the predicted data
      predictionDataRAINBOW[t] <- resEM3$y.pred[t]
    }
    
    # resEM3$weights
    predictData <- (predictionDataRAINBOW)
    obsData <- (y[,i])
    
    # calculate the R2 and RMSE
    correlation <- cor(obsData, predictData)
    R2 <- 1 - sum((obsData - predictData) ^ 2) / sum((obsData - mean(obsData)) ^ 2)
    RMSE <- sqrt(sum((obsData - predictData) ^ 2) / length(obsData))
    VU <- resEM3$Vu
    VE <- resEM3$Ve
    h2 <-  VU/(VU+VE)
    
    resultsum<- c(correlation, R2, RMSE,VU,VE,h2)
    resultsum<- as.matrix(resultsum)
    colnames(resultsum) <-trait.name
    return(resultsum)
  }
  close(pb)
  stopCluster(cl) 

  var.pheno.all <- res
  rownames(var.pheno.all) <- c("Correlation", "R2", "RMSE","varU","varE","h2")
  colnames(var.pheno.all) <- colnames(y)[2:ncol(y)]

  return(var.pheno.all)
}
toc()

resultModelname <- names
resultEachModel <- matrix(NA, nrow = length(ZETAlist), ncol = ncol(y)-1)
rownames(resultEachModel) <- names
colnames(resultEachModel) <- colnames(y)[2:ncol(y)]

#index p generator
for (n in 1:length(names)){
  
  resultEachModel[n,]<- xr[[n]][1,]
  
  if (n == 1){
    p <- names[1]
  }
  else{
    p  <- paste(p,names[n],sep="")
  }
}
print(p)

names(xr) <- names
resultEachModel_all<- xr


```

csv
```{R,eval=TRUE}
write.csv(resultEachModel, here("out",paste0("2019_blup",p,"_OneOut_c.csv" )))

write.csv(resultEachModel_all, here("out",paste0("2019_blup_ResAll_",p,"_OneOut_c.csv" )))
```



result plot
```{R,fig.dim = c(8, 4)}

#pred.all<-resultEachModel
pred.all <- read.csv( here("out",paste0("2019_blup",p,"_OneOut_c.csv" )),row.names=1)

model.name <- c("G", "Micro", "PredMet_f19","PredMet_f20", "TrueMet", "G+Micro", "G+Micro+PredMet_f19","G+Micro+PredMet_f20","G+Micro+TrueMet")
trait.name <- colnames(pred.all)
df.all <- NULL

for(i in 1:length(trait.name)) {
  
  pred <-  pred.all[,i]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}

df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- colnames(pred.all)
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge")  + ggtitle("Yield Prediction in 2019")
print(g)
```

