---
title: "Untitled"
output: html_document
date: "2023-09-08"
---
## 2.1 Model Build for 2020 Met Prediction 
Oneout 45 ver2
Inter and inner year prediction by BLUP   
Drought and Control
We tried the following models     
- G -> Met  (2019->2020)  
- G + Micro -> Met (2019->2020)  
- G + Micro -> Met (2020->2020)  

required packages
```{r, message =F}
require(BGLR)
require(here)
require(ggplot2)
require(reshape2)
require(gridExtra)
library(readr)
library(stringr)
library(ggsci)
library(RAINBOWR)
library(lubridate)
library(foreach)
library(future)
library(doFuture)
library(doRNG)
library(tictoc)
library(doSNOW)
```

seed
```{r, message =F}
# save or read the seed
seedIndCsv <-  here("out","seedInd.csv")
if (file.exists(seedIndCsv)) {
  seedInd <- read.csv(seedIndCsv, row.names = 1, header = T)
  seedInd <- c(as.matrix(seedInd))
} else {
  seedInd <- sample(1:500, 10, replace = F)
  write.csv(x = seedInd, file =  here("out","seedInd.csv"))
}
```

read phenotypic data
```{r}
pheno18 <- read.csv(here("2018", "shoot_blup_all_2018.csv"), row.names = 1)
pheno19 <- read.csv(here("2019", "shoot_blup_all_2019.csv"), row.names = 1)
pheno20 <- read.csv(here("2020", "shoot_blup_all_2020.csv"), row.names = 1)

plot18<-rownames(pheno18)
plot19<-rownames(pheno19)
plot20<-rownames(pheno20)

var18<-pheno18$var.id
var19<-pheno19$var.id
var20<-pheno20$var.id
```

read genomic relationship matrix data
```{r}
grm <- readRDS(here("data", "grm_2.rds"))
head(grm)[,1:3]
```

read metabolomic data
```{r}
met<- read.csv(here("2019","2019_Tottori_Jul_RootMetabolome_X.csv"))
rownames(met) <- paste0(substr(as.matrix(met[7]),1,2),".",sprintf("%03d",as.matrix(met[8])))
met19 <- met[,10:ncol(met)]
colnames(met19)<- sub("M","X",colnames(met19))

met <- read.csv(here("2020", "2020_Tottori_Main_RootMetabolome.csv"))
rownames(met) <- paste0(substr(as.matrix(met[7]),1,2),".",sprintf("%03d",as.matrix(met[8])))
met20 <- met[,10:ncol(met)]

s_c <- colnames(met19) %in% colnames(met20)
met19<- met19[,s_c]
s_c <- colnames(met20) %in% colnames(met19)
met20<- met20[,s_c]
#table(colnames(met20) == colnames(met19))
```

read microbiome rarificated data
```{r}
com <- read.table(here("2018", "table-from-biom-7-2018-after.txt"), row.names = 1)
rownames(com) <- gsub(";",".",rownames(com))
com18<- com
colnames(com18) <- cbind(plot18[201:400],plot18[601:800])

com <- read.csv(here("2019", "table-from-biom-7.csv"), row.names = 1)
rownames(com) <- gsub(";",".",rownames(com))
com19<- com

#comriken <- read.csv(here("2020", "table-from-biom-7-2020-after.csv"))
com <- read.csv(here("2020", "2020_Tottori_Main_Microbiome_Ratio.csv"))
rownames(com) <- paste0(substr(as.matrix(com[7]),1,2),".",sprintf("%03d",as.matrix(com[8])))
com <- com[,10:ncol(com)]
com20 <- t(com)

#s_c <- rownames(com19) %in% rownames(com20)
#com19<- com19[s_c,]
#s_c <- rownames(com20) %in% rownames(com19)
#com20<- com20[s_c,]

s_c <- (rownames(com19) %in% rownames(com20)) & (rownames(com19) %in% rownames(com18))
com19<- com19[s_c,]
s_c <- rownames(com20) %in% rownames(com19)
com20<- com20[s_c,]
s_c <- rownames(com18) %in% rownames(com20)
com18<- com18[s_c,]

dim(com18)
dim(com19)
dim(com20)
```


### Drought

```{r}
CD ="W4"
```


select the lines which has pheno, grm, met, micro data in 2019 and 2020
```{r}
selector.grm1 <- pheno18$var.id %in% rownames(grm)
selector.com1 <-rownames(pheno18) %in% colnames(com18)

selector.grm2 <- pheno19$var.id %in% rownames(grm)
selector.com2 <-rownames(pheno19) %in% colnames(com19)

selector.grm3 <- pheno20$var.id %in% rownames(grm)
selector.com3 <-rownames(pheno20) %in% colnames(com20)


pl<- list(pheno18,pheno19,pheno20)
pl.sel<- list()

for (i in 2:3){
pheno<- pl[[i]]

if (i==1) {
  selector.grm <- selector.grm1
  selector.com <- selector.com1
}

else if (i==2) {
  selector.grm <- selector.grm2
  selector.com <- selector.com2
}

else if (i==3) {
  selector.grm <- selector.grm3
  selector.com <- selector.com3
}


pheno.sel <- pheno[selector.grm & selector.com, ]
#head(pheno.sel)
print(dim(pheno.sel))

selector.cd <- substr(rownames(pheno.sel), 1, 2) == CD 
pheno.sel.cd <- pheno.sel[selector.cd, ]
dim(pheno.sel.cd)

plot.id <- rownames(pheno.sel.cd)
rownames(pheno.sel.cd)<-pheno.sel.cd$var.id
pheno.sel.cd$var.id <- plot.id
colnames(pheno.sel.cd)[1]<- "plot.id"
sg <- rownames(grm) %in% rownames(pheno.sel.cd)
gv<-rownames(grm[sg,sg])
pheno.sel.cd<- pheno.sel.cd[gv,]
print(dim(pheno.sel.cd))
pl.sel[[i]]<- pheno.sel.cd
}

#psc18<-  pl.sel[[1]]
psc19<-  pl.sel[[2]] 
psc20<-  pl.sel[[3]]



s_p <- rownames(psc19) %in% rownames(psc20)
psc19<- psc19[s_p,]
s_p <- rownames(psc20) %in% rownames(psc19)
psc20<- psc20[s_p,]

s_p <- colnames(psc19) %in% colnames(psc20)
psc19<- psc19[,s_p]
s_p <- colnames(psc20) %in% colnames(psc19)
psc20<- psc20[,s_p]

table(rownames(psc19) == rownames(psc20))

```




2019 
```{r}
var.id <- rownames(psc19)
grm.cd <- grm[var.id, var.id]
plot.id  <- psc19$plot.id
com19.cd <- t(com19[, plot.id])
com19.cd <- scale(com19.cd[, apply(com19.cd, 2, sd) > 0])
#met19ns.cd <- met19[plot.id, ]
met19.cd <- scale(met19[plot.id, ])

```

2020
```{r, message =F}
var.id <- rownames(psc20)
grm.cd <- grm[var.id, var.id]
plot.id  <- psc20$plot.id
com20.cd <- t(com20[, plot.id])
com20.cd <- scale(com20.cd[, apply(com20.cd, 2, sd) > 0])
#met20ns.cd <- met20[plot.id, ]
met20.cd <- scale(met20[plot.id, ])
```

Save the targeted Met 
```{r, message =F}
dim(met20.cd)
dim(met19.cd)
write.csv(met20.cd,here("out","met20d.csv"))
write.csv(met19.cd,here("out","met19d.csv"))
```


### Drought

```{r}
CD ="W1"
```


select the lines which has pheno, grm, met, micro data in 2019 and 2020
```{r}
selector.grm1 <- pheno18$var.id %in% rownames(grm)
selector.com1 <-rownames(pheno18) %in% colnames(com18)

selector.grm2 <- pheno19$var.id %in% rownames(grm)
selector.com2 <-rownames(pheno19) %in% colnames(com19)

selector.grm3 <- pheno20$var.id %in% rownames(grm)
selector.com3 <-rownames(pheno20) %in% colnames(com20)


pl<- list(pheno18,pheno19,pheno20)
pl.sel<- list()

for (i in 2:3){
pheno<- pl[[i]]

if (i==1) {
  selector.grm <- selector.grm1
  selector.com <- selector.com1
}

else if (i==2) {
  selector.grm <- selector.grm2
  selector.com <- selector.com2
}

else if (i==3) {
  selector.grm <- selector.grm3
  selector.com <- selector.com3
}


pheno.sel <- pheno[selector.grm & selector.com, ]
#head(pheno.sel)
print(dim(pheno.sel))

selector.cd <- substr(rownames(pheno.sel), 1, 2) == CD 
pheno.sel.cd <- pheno.sel[selector.cd, ]
dim(pheno.sel.cd)

plot.id <- rownames(pheno.sel.cd)
rownames(pheno.sel.cd)<-pheno.sel.cd$var.id
pheno.sel.cd$var.id <- plot.id
colnames(pheno.sel.cd)[1]<- "plot.id"
sg <- rownames(grm) %in% rownames(pheno.sel.cd)
gv<-rownames(grm[sg,sg])
pheno.sel.cd<- pheno.sel.cd[gv,]
print(dim(pheno.sel.cd))
pl.sel[[i]]<- pheno.sel.cd
}

#psc18<-  pl.sel[[1]]
psc19<-  pl.sel[[2]] 
psc20<-  pl.sel[[3]]



s_p <- rownames(psc19) %in% rownames(psc20)
psc19<- psc19[s_p,]
s_p <- rownames(psc20) %in% rownames(psc19)
psc20<- psc20[s_p,]

s_p <- colnames(psc19) %in% colnames(psc20)
psc19<- psc19[,s_p]
s_p <- colnames(psc20) %in% colnames(psc19)
psc20<- psc20[,s_p]

table(rownames(psc19) == rownames(psc20))

```




2019 
```{r}
var.id <- rownames(psc19)
grm.cd <- grm[var.id, var.id]
plot.id  <- psc19$plot.id
com19.cd <- t(com19[, plot.id])
com19.cd <- scale(com19.cd[, apply(com19.cd, 2, sd) > 0])
#met19ns.cd <- met19[plot.id, ]
met19.cd <- scale(met19[plot.id, ])

```

2020
```{r, message =F}
var.id <- rownames(psc20)
grm.cd <- grm[var.id, var.id]
plot.id  <- psc20$plot.id
com20.cd <- t(com20[, plot.id])
com20.cd <- scale(com20.cd[, apply(com20.cd, 2, sd) > 0])
#met20ns.cd <- met20[plot.id, ]
met20.cd <- scale(met20[plot.id, ])
```


Save the targeted Met 
```{r, message =F}
dim(met20.cd)
dim(met19.cd)
write.csv(met20.cd,here("out","met20c.csv"))
write.csv(met19.cd,here("out","met19c.csv"))
```


