---
title: "61_2"
author: "Hayato Yoshioka"
date: "2023-12-13"
output:
  pdf_document: default
  html_document: default
---


RF with RF

required packages
```{r, message =F}
require(BGLR)
library(dplyr)
require(here)
require(ggplot2)
# require(reshape2)
# require(gridExtra)
# library(readr)
# library(stringr)
# library(ggsci)
library(RAINBOWR)
# library(lubridate)
library(foreach)
library(future)
library(doFuture)
# library(doRNG)
library(tictoc)
library(doSNOW)
library(purrr)
source("Script/MyFunctions.R")
# library(vegan)
# library(VARshrink)
# library(ggplot2)
# library(glmnet)
# library(lars)
require(ranger)
# require(ggrepel)
# require(tidyverse)
getwd()
```



read phenotypic data
```{r}
pheno18 <- read.csv(here("2018", "shoot_blup_all_2018.csv"), row.names = 1)
pheno19 <- read.csv(here("2019", "shoot_blup_all_2019.csv"), row.names = 1)
pheno20 <- read.csv(here("2020", "shoot_blup_all_2020.csv"), row.names = 1)

plot18<-rownames(pheno18)
plot19<-rownames(pheno19)
plot20<-rownames(pheno20)

var18<-pheno18$var.id
var19<-pheno19$var.id
var20<-pheno20$var.id
```

read genomic relationship matrix data
```{r}
grm <- readRDS(here("data", "grm_2.rds"))
head(grm)[,1:3]
```


read metabolomic data
```{r}
met<- read.csv(here("2019","2019_Tottori_Jul_RootMetabolome_X.csv"))
rownames(met) <- paste0(substr(as.matrix(met[7]),1,2),".",sprintf("%03d",as.matrix(met[8])))
met19 <- met[,10:ncol(met)]
colnames(met19)<- sub("M","X",colnames(met19))

met <- read.csv(here("2020", "2020_Tottori_Main_RootMetabolome.csv"))
rownames(met) <- paste0(substr(as.matrix(met[7]),1,2),".",sprintf("%03d",as.matrix(met[8])))
met20 <- met[,10:ncol(met)]

s_c <- colnames(met19) %in% colnames(met20)
met19<- met19[,s_c]
s_c <- colnames(met20) %in% colnames(met19)
met20<- met20[,s_c]
table(colnames(met20) == colnames(met19))

dim(met19)
dim(met20)
```

read met index

```{r}
metind<- read.csv(here("data","Metabolome_index.csv"))
metindex<- matrix(metind[,2],583,1)
rownames(metindex)<- metind[1:583,1]
```


read microbiome rarificated data
```{r}
com <- read.table(here("2018", "table-from-biom-7-2018-after.txt"), row.names = 1)
rownames(com) <- gsub(";",".",rownames(com))
com18<- com
colnames(com18) <- cbind(plot18[201:400],plot18[601:800])

com <- read.csv(here("2019", "table-from-biom-7.csv"), row.names = 1)
rownames(com) <- gsub(";",".",rownames(com))
com19<- com

#comriken <- read.csv(here("2020", "table-from-biom-7-2020-after.csv"))
com <- read.csv(here("2020", "2020_Tottori_Main_Microbiome_Ratio.csv"))
rownames(com) <- paste0(substr(as.matrix(com[7]),1,2),".",sprintf("%03d",as.matrix(com[8])))
com <- com[,10:ncol(com)]
com20 <- t(com)

#s_c <- rownames(com19) %in% rownames(com20)
#com19<- com19[s_c,]
#s_c <- rownames(com20) %in% rownames(com19)
#com20<- com20[s_c,]

s_c <- (rownames(com19) %in% rownames(com20)) & (rownames(com19) %in% rownames(com18))
com19<- com19[s_c,]
s_c <- rownames(com20) %in% rownames(com19)
com20<- com20[s_c,]
s_c <- rownames(com18) %in% rownames(com20)
com18<- com18[s_c,]

dim(com18)
dim(com19)
dim(com20)
```

### Condition

```{r}
CD ="W4"

if (CD == "W4"){
  print(CD)
  cd<- "Drought"
  predmet20f19 <- read.csv(here("out", "20f19_predmet_G_blup_OneOut.csv"), row.names = 1)
  predmet19f20 <- read.csv(here("out", "19f20_predmet_G_blup_OneOut.csv"), row.names = 1)
  
  predmet19 <- read.csv(here("out", "19f19_predmet_G_blup_OneOut.csv"), row.names = 1)
  predmet20 <- read.csv(here("out", "20f20_predmet_G_blup_OneOut.csv"), row.names = 1)
  
  RF <- readRDS(here("out", "19f19_predMet_RF_OneOut_W4com.rds")) #com
  predmet19RF<-RF[["G"]]
  
  RF2 <- readRDS(here("out", "19f20_predMet_RF_OneOut_W4com.rds"))
  predmet19f20RF<-RF2[["G"]]

  } else if (CD == "W1"){
  print(CD)
  cd<- "Control"
  predmet20f19 <- read.csv(here("out", "20f19_predmet_G_blup_OneOut_c.csv"), row.names = 1)
  predmet19f20 <- read.csv(here("out", "19f20_predmet_G_blup_OneOut_c.csv"), row.names = 1)
  
  predmet19 <- read.csv(here("out", "19f19_predmet_G_blup_OneOut_c.csv"), row.names = 1)
  predmet20 <- read.csv(here("out", "20f20_predmet_G_blup_OneOut_c.csv"), row.names = 1)
  
  RF <- readRDS(here("out", "19f19_predMet_RF_OneOut_W1com.rds"))
  predmet19RF<-RF[["G"]]
  
  RF2 <- readRDS(here("out", "19f20_predMet_RF_OneOut_W1com.rds"))
  predmet19f20RF<-RF2[["G"]]
  
  } else {
  print("error")
  }

dim(predmet19)
#RF <- readRDS(here("out", "19f19_predMet_RF_OneOut_W4snp.rds"))
#predmet19RFsnp<-RF[["G+Micro"]] 

```


select the lines which has pheno, grm, met, micro data in 2019 and 2020
```{r}
selector.grm1 <- pheno18$var.id %in% rownames(grm)
selector.com1 <-rownames(pheno18) %in% colnames(com18)

selector.grm2 <- pheno19$var.id %in% rownames(grm)
selector.com2 <-rownames(pheno19) %in% colnames(com19)

selector.grm3 <- pheno20$var.id %in% rownames(grm)
selector.com3 <-rownames(pheno20) %in% colnames(com20)


pl<- list(pheno18,pheno19,pheno20)
pl.sel<- list()

for (i in 2:3){
pheno<- pl[[i]]

if (i==1) {
  selector.grm <- selector.grm1
  selector.com <- selector.com1
}

else if (i==2) {
  selector.grm <- selector.grm2
  selector.com <- selector.com2
}

else if (i==3) {
  selector.grm <- selector.grm3
  selector.com <- selector.com3
}


pheno.sel <- pheno[selector.grm & selector.com, ]
#head(pheno.sel)
print(dim(pheno.sel))

selector.cd <- substr(rownames(pheno.sel), 1, 2) == CD 
pheno.sel.cd <- pheno.sel[selector.cd, ]
dim(pheno.sel.cd)

plot.id <- rownames(pheno.sel.cd)
rownames(pheno.sel.cd)<-pheno.sel.cd$var.id
pheno.sel.cd$var.id <- plot.id
colnames(pheno.sel.cd)[1]<- "plot.id"
sg <- rownames(grm) %in% rownames(pheno.sel.cd)
gv<-rownames(grm[sg,sg])
pheno.sel.cd<- pheno.sel.cd[gv,]
print(dim(pheno.sel.cd))
pl.sel[[i]]<- pheno.sel.cd
}

#psc18<-  pl.sel[[1]]
psc19<-  pl.sel[[2]] 
psc20<-  pl.sel[[3]]



s_p <- rownames(psc19) %in% rownames(psc20)
psc19<- psc19[s_p,]
s_p <- rownames(psc20) %in% rownames(psc19)
psc20<- psc20[s_p,]

#s_p <- colnames(psc19) %in% colnames(psc20)
#psc19<- psc19[,s_p]
#s_p <- colnames(psc20) %in% colnames(psc19)
#psc20<- psc20[,s_p]

table(rownames(psc19) == rownames(psc20))

```



2019 
```{r}
var.id <- rownames(psc19)
grm.cd <- grm[var.id, var.id]
plot.id  <- psc19$plot.id
com19.cd <- t(com19[, plot.id])
com19.cd <- scale(com19.cd[, apply(com19.cd, 2, sd) > 0])
#met19ns.cd <- met19[plot.id, ]
met19.cd <- scale(met19[plot.id, ])
#predmet19ns<-predmet19
predmet19<-scale(predmet19)
#genome.cd<- genome[var.id,]
predmet19RF<-scale(predmet19RF)
predmet19f20RF<-scale(predmet19f20RF)
```


2020
```{r, message =F}
var.id <- rownames(psc20)
grm.cd <- grm[var.id, var.id]
plot.id  <- psc20$plot.id
com20.cd <- t(com20[, plot.id])
com20.cd <- scale(com20.cd[, apply(com20.cd, 2, sd) > 0])
#met20ns.cd <- met20[plot.id, ]
met20.cd <- scale(met20[plot.id, ])
#predmetns20<-predmet20
predmet20<-scale(predmet20)
#predmetns20f19<-predmet20f19
predmet20f19<-scale(predmet20f19)
predmet19f20<-scale(predmet19f20)
#genome.cd<- genome[var.id,]
```


Integrate + RM
```{r, message =F}
psc <- rbind(psc19,psc19)

s_c <- colnames(com19.cd) %in% colnames(com20.cd)
com19.cd<- com19.cd[,s_c]
s_c <- colnames(com20.cd) %in% colnames(com19.cd)
com20.cd<- com20.cd[,s_c]

s_c <- colnames(com19.cd) %in% colnames(com20.cd)
com19.cd<- com19.cd[,s_c]
s_c <- colnames(com20.cd) %in% colnames(com19.cd)
com20.cd<- com20.cd[,s_c]

mrm19.cd <- tcrossprod(com19.cd) / ncol(com19.cd)
mrm20.cd <- tcrossprod(com20.cd) / ncol(com20.cd)

com.cd<- rbind(com19.cd,com20.cd)
rownames(com.cd)<-rownames(psc)
mrm.cd <- tcrossprod(com.cd) / ncol(com.cd)

metrm19.cd <- tcrossprod(met19.cd) / ncol(met19.cd)
metrm20.cd <- tcrossprod(met20.cd) / ncol(met20.cd)

metPrm19.cd <- tcrossprod(predmet19) / ncol(predmet19)
metPrm20.cd <- tcrossprod(predmet20) / ncol(predmet20)

metPrm20f19.cd <- tcrossprod(predmet20f19) / ncol(predmet20f19)
metPrm19f20.cd <- tcrossprod(predmet19f20) / ncol(predmet19f20)

metPrm19RF.cd <- tcrossprod(predmet19RF) / ncol(predmet19RF)
metPrm19f20RF.cd <- tcrossprod(predmet19f20RF) / ncol(predmet19f20RF)

#metns.cd <- rbind(met19ns.cd,met20ns.cd)
met.cd<- rbind(met19.cd,met20.cd)
rownames(met.cd)<-rownames(psc)
metrm.cd <- tcrossprod(met.cd) / ncol(met.cd)
```

```{R}
comn<-  paste0(rep("OTU_",ncol(com19.cd)),1:ncol(com19.cd))
comnameL <-colnames(com19.cd)
colnames(com19.cd)<- comn
```




```{r, message =F, include=TRUE,eval=TRUE}
K1 <- grm.cd
K2 <- com19.cd
K3 <- met19.cd
K8 <- predmet19
K9 <- predmet19f20
#K10 <- RDA_M
K11 <- predmet19RF
K12 <- predmet19f20RF

K1_8 <- list(K1=K1,K8=K8)
K1_9 <- list(K1=K1,K9=K9)
K1_11<- list(K1=K1,K11=K11)
K1_12<- list(K1=K1,K12=K12)
K1_3 <- list(K1=K1,K3=K3)

```
KZ1,KZ3,KZ8,KZ9,KZ11,KZ12,KZ1_8,KZ1_9,KZ1_11,KZ1_12,KZ1_3

### Yield 2019model
```{r, message =F, include=TRUE,eval=TRUE}

RFlist <- list(K1=list(K1=K1),
               K3=list(K3=K3),
               K8=list(K8=K8),
               K9=list(K9=K9),
               K11=list(K11=K11),
               K12=list(K12=K12),
               K1_8=K1_8,
               K1_9=K1_9,
               K1_11=K1_11,
               K1_12=K1_12,
               K1_3=K1_3)

Y <- psc19[,-1]

tic()
res <- getRF(RFlist,Y)
toc()

saveRDS(res, here("out", paste0("yPredYield_RF_", CD, "com_g.RDS")))

```
# read 
```{r}
res<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_g.RDS")))
```

### metpred 
```{}
#RFlist <- list(Bpred_B=list(Bpred=Bpred))

RFlist <- list(K8=list(Bpred=K8),
               K9=list(Bpred=K9),
               K11=list(Bpred=K11),
               K12=list(Bpred=K12))

Y <- psc19[,-1]

tic()
res_bpred <- getRF(RFlist,Y)
toc()
saveRDS(res_bpred, here("out", paste0("yPredYield_RF_", CD, "com_bpred.RDS")))

tic()
res_bpred_b <- getRF(RFlist,Y,dummy="Bpred",Tv=K3)
toc()
saveRDS(res_bpred_b, here("out", paste0("yPredYield_RF_", CD, "com_bpred_b.RDS")))

#SaveRDS(res, here("out", paste0("yPredYield_RF_", CD, "dummy.RDS")))
```

# read 
```{}
res_bpred<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred.RDS")))
res_bpred_b<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred_b.RDS")))

```

### metpred 12
```{}
#RFlist <- list(Bpred_B=list(Bpred=Bpred))
K1_2_8 <- list(K1=K1,K2=K2,Bpred=K8)
K1_2_9 <- list(K1=K1,K2=K2,Bpred=K9)
K1_2_11<- list(K1=K1,K2=K2,Bpred=K11)
K1_2_12<- list(K1=K1,K2=K2,Bpred=K12)

RFlist <- list(K1_2_8=K1_2_8,
               K1_2_9=K1_2_9,
               K1_2_11=K1_2_11,
               K1_2_12=K1_2_12)

Y <- psc19[,-1]

tic()
res_bpred <- getRF(RFlist,Y)
toc()
saveRDS(res_bpred, here("out", paste0("yPredYield_RF_", CD, "com_bpred_gm.RDS")))

tic()
res_bpred_b <- getRF(RFlist,Y,dummy="Bpred",Tv=K3)
toc()
saveRDS(res_bpred_b, here("out", paste0("yPredYield_RF_", CD, "com_bpred_b_gm.RDS")))

#SaveRDS(res, here("out", paste0("yPredYield_RF_", CD, "dummy.RDS")))
```

# read 
```{}
res_bpred<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred_gm.RDS")))
res_bpred_b<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred_b_gm.RDS")))
```

all
```{R,fig.dim = c(8, 4)}
#p<- c("KZ1KZ2KZ3KZ8KZ9KZ11KZ1_2KZ1_2_8KZ1_2_9KZ1_2_11KZ1_2_12KZ1_2_3")
#pred.all<-resultEachModel
#pred.all <- read.csv(here("out",paste0("2019_RF",p,"_OneOut_",CD,".csv")),row.names=1)

p<-res$p
pred.all<-res$resultEachModel

model.name <- c("G","TrueMet","PredMetBlupf19","PredMetBlupf20","PredMetRFf19","PredMetRFf20","G+PredMetBlupf19","G+PredMetBlupf20","G+PredMetRFf19","G+PredMetRFf20","G+TrueMet")

trait.name <- colnames(pred.all) %>% sort() #sort
pred.all<- data.frame(pred.all) %>% select(trait.name)
df.all <- NULL


for(i in 1:length(trait.name)) {
  
  pred <-  pred.all[,i]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}



df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- colnames(pred.all)
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge")  
g <- g + ggtitle(paste0("Yield Prediction RF in 2019 ",cd))
g <- g + ylab("COR")
g <- g + xlab("")

g <- g + theme(axis.text.x = element_text(angle = 60, hjust=1))

print(g)

```

CD="W4"
cd<-"Drought"

# result plot
raw
```{R}
res<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_g.RDS")))
p<-res$p
pred.all<-res$resultEachModel

pred.all<- pred.all[c(1,7,8,9,10,11),]
model.name <- c("G","G+PredMetBlupf19","G+PredMetBlupf20","G+PredMetRFf19","G+PredMetRFf20","G+TrueMet")

trait.name <- colnames(pred.all) %>% sort() #sort
pred.all<- data.frame(pred.all) %>% select(trait.name)

df.all <- NULL

for(i in 1:length(trait.name)) {
  pred <-  pred.all[,colnames(pred.all)==trait.name[i]]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}


df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- trait.name # trait
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge") +ylim(0,0.9) 
g <- g + ggtitle(paste0("Yield Prediction RF in 2019 ",cd))
g <- g + ylab("COR")
g <- g + xlab("")

g <- g + theme(axis.text.x = element_text(angle = 60, hjust=1))

print(g)
```


raw bpred
```{}
CD="W4"
cd<-"Drought"


res_bpred<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred.RDS")))


p<-res_bpred$p
pred.all<-res_bpred$resultEachModel

#pred.all<- pred.all[c(1,7,8,9,10,11,12),]
model.name <- c("PredMetBLUPf19","PredMetBLUPf20","PredMetRF_f19","PredMetRF_f20")

trait.name <- colnames(pred.all) %>% sort() #sort
pred.all<- data.frame(pred.all) %>% select(trait.name)

df.all <- NULL

for(i in 1:length(trait.name)) {
  pred <-  pred.all[,colnames(pred.all)==trait.name[i]]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}

df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- trait.name # trait
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge") +ylim(0,0.9) 
g <- g + ggtitle(paste0("Yield Prediction RF in 2019 ",cd))
g <- g + ylab("COR")


g <- g + theme(axis.text.x = element_text(angle = 60, hjust=1))

print(g)

########


res_bpred_b<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred_b.RDS")))

p<-res_bpred_b$p
pred.all<-res_bpred_b$resultEachModel

#pred.all<- pred.all[c(1,7,8,9,10,11,12),]
model.name <- c("PredMetBLUPf19","PredMetBLUPf20","PredMetRF_f19","PredMetRF_f20")

trait.name <- colnames(pred.all) %>% sort() #sort
pred.all<- data.frame(pred.all) %>% select(trait.name)

df.all <- NULL

for(i in 1:length(trait.name)) {
  pred <-  pred.all[,colnames(pred.all)==trait.name[i]]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}

df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- trait.name # trait
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge") +ylim(0,0.9) 
g <- g + ggtitle(paste0("Yield Prediction RF in 2019 ",cd," (pred by True Met)"))
g <- g + ylab("COR")


g <- g + theme(axis.text.x = element_text(angle = 60, hjust=1))

print(g)


CD="W1"
cd<-"Control"



res_bpred<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred.RDS")))


p<-res_bpred$p
pred.all<-res_bpred$resultEachModel

#pred.all<- pred.all[c(1,7,8,9,10,11,12),]
model.name <- c("PredMetBLUPf19","PredMetBLUPf20","PredMetRF_f19","PredMetRF_f20")

trait.name <- colnames(pred.all) %>% sort() #sort
pred.all<- data.frame(pred.all) %>% select(trait.name)

df.all <- NULL

for(i in 1:length(trait.name)) {
  pred <-  pred.all[,colnames(pred.all)==trait.name[i]]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}

df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- trait.name # trait
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge") +ylim(0,0.9) 
g <- g + ggtitle(paste0("Yield Prediction RF in 2019 ",cd))
g <- g + ylab("COR")


g <- g + theme(axis.text.x = element_text(angle = 60, hjust=1))

print(g)

########


res_bpred_b<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred_b.RDS")))

p<-res_bpred_b$p
pred.all<-res_bpred_b$resultEachModel

#pred.all<- pred.all[c(1,7,8,9,10,11,12),]
model.name <- c("PredMetBLUPf19","PredMetBLUPf20","PredMetRF_f19","PredMetRF_f20")

trait.name <- colnames(pred.all) %>% sort() #sort
pred.all<- data.frame(pred.all) %>% select(trait.name)

df.all <- NULL

for(i in 1:length(trait.name)) {
  pred <-  pred.all[,colnames(pred.all)==trait.name[i]]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}

df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- trait.name # trait
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge") +ylim(0,0.9) 
g <- g + ggtitle(paste0("Yield Prediction RF in 2019 ",cd," (pred by True Met)"))
g <- g + ylab("COR")


g <- g + theme(axis.text.x = element_text(angle = 60, hjust=1))

print(g)

```




```{}

CD="W4"
cd<-"Drought"

res_bpred<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred_gm.RDS")))
res_bpred_b<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred_b_gm.RDS")))

p<-res_bpred$p
pred.all<-res_bpred$resultEachModel

#pred.all<- pred.all[c(1,7,8,9,10,11,12),]
model.name <- c("G+Micro+PredMetBLUPf19","G+Micro+PredMetBLUPf20","G+Micro+PredMetRF_f19","G+Micro+PredMetRF_f20")
trait.name <- colnames(pred.all) %>% sort() #sort
pred.all<- data.frame(pred.all) %>% select(trait.name)

df.all <- NULL

for(i in 1:length(trait.name)) {
  pred <-  pred.all[,colnames(pred.all)==trait.name[i]]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}

df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- trait.name # trait
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge") +ylim(0,0.9) 
g <- g + ggtitle(paste0("Yield Prediction RF in 2019 ",cd))
g <- g + ylab("COR")


g <- g + theme(axis.text.x = element_text(angle = 60, hjust=1))

print(g)

########


p<-res_bpred_b$p
pred.all<-res_bpred_b$resultEachModel

#pred.all<- pred.all[c(1,7,8,9,10,11,12),]
model.name <- c("G+Micro+PredMetBLUPf19","G+Micro+PredMetBLUPf20","G+Micro+PredMetRF_f19","G+Micro+PredMetRF_f20")

trait.name <- colnames(pred.all) %>% sort() #sort
pred.all<- data.frame(pred.all) %>% select(trait.name)

df.all <- NULL

for(i in 1:length(trait.name)) {
  pred <-  pred.all[,colnames(pred.all)==trait.name[i]]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}

df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- trait.name # trait
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge") +ylim(0,0.9) 
g <- g + ggtitle(paste0("Yield Prediction RF in 2019 ",cd," (pred by True Met)"))
g <- g + ylab("COR")


g <- g + theme(axis.text.x = element_text(angle = 60, hjust=1))

print(g)


CD="W1"
cd<-"Control"

res_bpred<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred_gm.RDS")))
res_bpred_b<-readRDS(here("out", paste0("yPredYield_RF_", CD, "com_bpred_b_gm.RDS")))

p<-res_bpred$p
pred.all<-res_bpred$resultEachModel

#pred.all<- pred.all[c(1,7,8,9,10,11,12),]
model.name <- c("G+Micro+PredMetBLUPf19","G+Micro+PredMetBLUPf20","G+Micro+PredMetRF_f19","G+Micro+PredMetRF_f20")

trait.name <- colnames(pred.all) %>% sort() #sort
pred.all<- data.frame(pred.all) %>% select(trait.name)

df.all <- NULL

for(i in 1:length(trait.name)) {
  pred <-  pred.all[,colnames(pred.all)==trait.name[i]]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}

df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- trait.name # trait
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge") +ylim(0,0.9) 
g <- g + ggtitle(paste0("Yield Prediction RF in 2019 ",cd))
g <- g + ylab("COR")


g <- g + theme(axis.text.x = element_text(angle = 60, hjust=1))

print(g)

########


p<-res_bpred_b$p
pred.all<-res_bpred_b$resultEachModel

#pred.all<- pred.all[c(1,7,8,9,10,11,12),]
model.name <- c("G+Micro+PredMetBLUPf19","G+Micro+PredMetBLUPf20","G+Micro+PredMetRF_f19","G+Micro+PredMetRF_f20")

trait.name <- colnames(pred.all) %>% sort() #sort
pred.all<- data.frame(pred.all) %>% select(trait.name)

df.all <- NULL

for(i in 1:length(trait.name)) {
  pred <-  pred.all[,colnames(pred.all)==trait.name[i]]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}

df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- trait.name # trait
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge") +ylim(0,0.9) 
g <- g + ggtitle(paste0("Yield Prediction RF in 2019 ",cd," (pred by True Met)"))
g <- g + ylab("COR")


g <- g + theme(axis.text.x = element_text(angle = 60, hjust=1))

print(g)

```


rm (old version)
```{}

p<- c("K1K2K3K8K9K11K1_2K1_2_8K1_2_9")
pred.all <- read.csv(here("out",paste0("2019_RF",p,"_OneOut_",CD,".csv")),row.names=1)


pred.all<- pred.all[c(1,7,8,9,10,11,12),]
model.name <- c("G","G+Micro","G+Micro+PredMetBLUPf19","G+Micro+PredMetBLUPf20","G+Micro+PredMetRF_f19","G+Micro+PredMetRF_f20","G+MIcro+TrueMet")

trait.name <- colnames(pred.all) %>% sort() #sort
pred.all<- data.frame(pred.all) %>% select(trait.name)

df.all <- NULL

for(i in 1:length(trait.name)) {
  pred <-  pred.all[,colnames(pred.all)==trait.name[i]]
  df <- data.frame(trait = trait.name[i],model = model.name, mean = pred)
  df.all <- rbind(df.all, df)
}


df.all[df.all < 0] <- 0
df.all$model <- factor(df.all$model, levels = model.name)
df.all$trait <- factor(df.all$trait)
levels(df.all$trait) <- trait.name # trait
g <- ggplot(df.all)
g <- g + geom_bar(aes(x = trait, y = mean, fill = model), 
                  stat = "identity",  position = "dodge") +ylim(0,0.9) 
g <- g + ggtitle(paste0("Yield Prediction RF in 2019 ",cd))
g <- g + ylab("COR")


g <- g + theme(axis.text.x = element_text(angle = 60, hjust=1))

print(g)
```





